Manuscript Title:\\with Forced Linebreak

### 2020-04-16 paper1.tex
include Guimera plots
Recent works
recent works

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

@@

\textbf{talk about how to map the original nanowire network on to a graph}.

@@

@@

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{figure/G_dG_t}
	\caption{}
	\label{fig:g_dg_t}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{figure/TE_dG}
	\caption{}
	\label{fig:te_dg}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{figure/TE_act_time}
	\caption{}
	\label{fig:te_act_time}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{figure/mod_dG}
	\caption{}
	\label{fig:mod_dg}
\end{figure}

@@

\section{\label{sec:level1} Discussion}

>>>>

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{bbold}
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

@@

\textbf{Talk about how to map the original nanowire network on to a graph. Cite Zdenka here}.

@@

\subsection{\label{sec:level2} Simulation}
When connected to external voltage biases, nanowire networks behave like traditional electrical networks. Each component in the network obeys Kirchhoff's law. Hence the voltage distribution across the network can be obtained by solving \cite{Dorfler2018}:

\begin{equation}
{\cal L}^\dagger V = I,
\end{equation}

where $\mathcal{L}^\dagger$ is the expanded graph Laplacian of the network, composed as:

\begin{equation}
	\cal L^\dagger = 
	\left[
	\begin{array}{c|c}
	\cal L&  C\\ 
	\hline
	C^T & \mathbb{0}  
	\end{array}
	\right],
\end{equation}

in which $\cal L$ is the graph Laplacian and $C$ represents the nodes (wires) connected to external electrodes.

\begin{equation}
{\cal L} = D - W
\end{equation}

@@

\subsection{\label{sec:level2} Communicability}
Communicability in a network represents .... \cite{Estrada2008}.

In this work communicability is calculated based on the weighted connections \cite{Crofts2009}. A symmetric matrix $M$ is generated to depict the communicability distribution, where $M_{i,j}$ represents the communicability between nodes $i$ and $j$. Therefore, $M$ reads:
\begin{equation}
M = \exp{(D^{-1/2} W D^{-1/2})}.
\end{equation}

@@

@@

@@

@@

\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{figure/time_series}
	\caption{}
	\label{fig:time_series}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{figure/time_align}
	\caption{}
	\label{fig:time_align}
\end{figure}

@@

The Guimera \textbf{cite here} plots can be displayed as follow:

\begin{figure}[h]
	\centering
	\includegraphics[width=1\linewidth]{figure/guimera_combine}
	\caption{}
	\label{fig:guimera_combine}
\end{figure}

\textbf{Have to match the color bars here.}

\newpage
\section{\label{sec:level1} Discussion}
